A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-10-25 sections/appendix/proportion_within_target_formula/main.tex
Minor fix in Markov chain formulas
For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

\section{Mean blocking time} \label{sec:appendix_mean_proportion}

@@

In addition, the set of accepting states for type 1 \(S_A^{(1)}\) and type 2 
\(S_A^{(2)}\) individuals defined in (\ref{eq:accepting_states_type_1}) and 
(\ref{eq:accepting_states_type_2}) are also needed here.
Note here that, \(S\) denotes the set of all states of the Markov chain model.

@@

\begin{equation}
    P(X^{(1)} < t) = \frac{\sum_{(u,v) \in S_A^{(1)}} P(X_{u,v}^{(1)} < t) 
    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(1)}} \pi_{u,v}}
\end{equation}

\begin{equation}
    P(X^{(2)} < t) = \frac{\sum_{(u,v) \in S_A^{(2)}} P(X_{u,v}^{(2)} < t) 
    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(2)}} \pi_{u,v}}
\end{equation}

>>>>

\section{Mean proportion of individuals within target} 
\label{sec:appendix_mean_proportion}

@@

In addition, the set of accepting states for type 1 (\(S_A^{(1)}\)) and type 2 
(\(S_A^{(2)}\)) individuals defined in (\ref{eq:accepting_states_type_1}) and 
(\ref{eq:accepting_states_type_2}) are also needed here.
Note here that, \(S\) denotes the set of all states of the Markov chain model.

@@

\begin{equation}
    P(X^{(1)} < t) = \frac{\sum_{(u,v) \in S_A^{(1)}} 
    P(X_{\mathcal{A}_1(u,v)}^{(1)} < t) 
    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(1)}} \pi_{u,v}}
\end{equation}

\begin{equation}
    P(X^{(2)} < t) = \frac{\sum_{(u,v) \in S_A^{(2)}} 
    P(X_{\mathcal{A}_2(u,v)}^{(2)} < t) 
    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(2)}} \pi_{u,v}}
\end{equation}

Note that \(\mathcal{A}_1(u,v)\) and \(\mathcal{A}_2(u,v)\) are defined in 
section \ref{sec:blocking_time} by equations \ref{eq:arriving_state_class_1} 
and \ref{eq:arriving_state_class_2}.

### 2021-10-25 sections/appendix/waiting_time_formula/main.tex
Minor fix in Markov chain formulas
For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

Finally, the mean waiting time can be calculated by summing over all expected 
waiting times of accepting states multiplied by the probability of being at that 
state and dividing by the probability of being in any accepting state.

\begin{equation} \label{eq:recursive_waiting_time_type_1}
    W^{(1)} = \frac{\sum_{(u,v) \in S_A^{(1)}} w^{(1)}(u,v) 
    \pi_{(u,v)}}{\sum_{(u,v) \in S_A^{(1)}} \pi_{(u,v)}}
\end{equation}

\begin{equation}\label{eq:recursive_waiting_time_type_2}
    W^{(2)} = \frac{\sum_{(u,v) \in S_A^{(2)}} w^{(2)}(u,v) \pi_{(u,v)}}
    {\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)}}
\end{equation}

>>>>

Finally, the mean waiting time can be calculated by summing over all expected 
waiting times of accepting states multiplied by the probability of being at that 
state and dividing by the probability of being in any accepting state.
Note here that \( \mathcal{A}_i \) is defined in section 
\ref{sec:blocking_time} by equations \ref{eq:arriving_state_class_1} and
\ref{eq:arriving_state_class_2}.

\begin{equation} \label{eq:recursive_waiting_time_type_1}
    W^{(1)} = \frac{\sum_{(u,v) \in S_A^{(1)}} w^{(1)}
    (\mathcal{A}_1(u,v)) \pi_{(u,v)}}
    {\sum_{(u,v) \in S_A^{(1)}} \pi_{(u,v)}}
\end{equation}

\begin{equation}\label{eq:recursive_waiting_time_type_2}
    W^{(2)} = \frac{\sum_{(u,v) \in S_A^{(2)}} w^{(2)}
    (\mathcal{A}_2(u,v)) \pi_{(u,v)}}
    {\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)}}
\end{equation}

### 2021-10-25 sections/queueing_model/blocking_time/main.tex
Minor fix in Markov chain formulas
For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

% TODO: Fix this equation by using the arriving state 
\begin{equation}\label{eq:algebraic_blocking_time}
    B = \frac{\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)} \; 
    b(u,v)}{\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)}}
\end{equation}

Here \(S_A^{(2)}\) is the set of accepting states of type 2 individuals (defined
in (\ref{eq:accepting_states_type_2})) and \(b(u,v)\) is the mean time that an 
individual will be blocked when the system is at state \((u,v)\). 
For all the states of the system \(b(u,v)\) is given by:

>>>>

\begin{equation}\label{eq:algebraic_blocking_time}
    B = \frac{\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)} \; 
    b(\mathcal{A}_2(u,v))}{\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)}}
\end{equation}

Here \(S_A^{(2)}\) is the set of accepting states of type 2 individuals (defined
in (\ref{eq:accepting_states_type_2})) and \(\mathcal{A}_i(u,v) \, i \in 
\{1, 2\} \) is the state that the model would go to when the system is at state 
\( (u,v) \) and a class \(i\) individual arrives.

\begin{equation}\label{eq:arriving_state_class_1}
    \mathcal{A}_1(u,v) = (u, v + 1)
\end{equation}
\begin{equation}\label{eq:arriving_state_class_2}
    \mathcal{A}_2(u,v) = 
    \begin{cases}
        (u, v + 1), & \text{if } v < T \\
        (u + 1, v), & \text{if } v \geq T \\
    \end{cases}
\end{equation}

The term \(b(u,v)\) is the mean time that an individual will be blocked when 
the system is at state \((u,v)\). 
For all the states of the system \(b(u,v)\) is given by:

### 2021-10-25 sections/queueing_model/proportion_within_target/main.tex
Apply alex's suggestion
Minor fix in Markov chain formulas
For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

\begin{equation}\label{eq:proportion_within_target_type_1}
    P(X^{(1)} < t) = \frac{\sum_{(u,v) \in S_A^{(1)}} P(X_{(u,v)}^{(1)} < t) 
    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(1)}} \pi_{u,v}}
\end{equation}

The proportion of type 2 individuals within a time target remains as:

\begin{equation}\label{eq:proportion_within_target_type_2}
    P(X^{(2)} < t) = \frac{\sum_{(u,v) \in S_A^{(2)}} P(X_{(u,v)}^{(2)} < t) 
    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(2)}} \pi_{u,v}}
\end{equation}

The overall proportion individuals within a time target (where \(P_{L'_1}\) and 
\(P_{L'_1}\) are defined in (\ref{eq:proportion_of_accepting_individuals})):

>>>>

\begin{equation}\label{eq:proportion_within_target_type_1}
    P(X^{(1)} < t) = \frac{\sum_{(u,v) \in S_A^{(1)}} 
    P(X_{\mathcal{A}_1(u,v)}^{(1)} < t) 
    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(1)}} \pi_{u,v}}
\end{equation}

The proportion of type 2 individuals within a time target:

\begin{equation}\label{eq:proportion_within_target_type_2}
    P(X^{(2)} < t) = \frac{\sum_{(u,v) \in S_A^{(2)}} 
    P(X_{\mathcal{A}_2(u,v)}^{(2)} < t) 
    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(2)}} \pi_{u,v}}
\end{equation}

The terms \(\mathcal{A}_1(u,v)\) and \(\mathcal{A}_2(u,v)\) are defined by
equations \ref{eq:arriving_state_class_1} and \ref{eq:arriving_state_class_2}
in section \ref{sec:blocking_time}.
The overall proportion individuals within a time target (where \(P_{L'_1}\) and 
\(P_{L'_1}\) are defined in (\ref{eq:proportion_of_accepting_individuals})):
